PM Mungbean meta-analysis

### 2020-12-21 02_Preliminary_analysis.Rmd
graph mean yield per trial grouped by treatmented non-treated

```{r ControlYield_AllTrials}
PM_MB_dat %>%
   filter(fungicide_ai == "control")%>%
   summarise(mean_yield = mean(grain_yield.t.ha.),
             minimum_yield = min(grain_yield.t.ha.),
             maximum_yield = max(grain_yield.t.ha.),
             yield_stdev = sd(grain_yield.t.ha.),
             yield_SE = sd(grain_yield.t.ha.)/
                              sqrt(n())) %>%
   kable(align = 'c',
   caption = "Average yield statistics for no spray contol plots"
)

@@

@@

```{r YieldGain_plot}
PM_MB_dat %>%
   filter(trial_ref %in% DMITrials)%>%  
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole"|
             fungicide_ai == "control")%>%
   mutate(spray_NoSpray = factor(ifelse(fungicide_ai == "control","control","Fungicide treated"))) %>%
   mutate(control_yield = ifelse(fungicide_ai == "control",grain_yield.t.ha.,NA))%>%
   group_by(trial_ref, location, year,spray_NoSpray)%>%
   summarise(yield_c = mean(control_yield),
             yield_gain_m = mean(yield_gain, na.rm = TRUE),
             yield_gain_se = sd(yield_gain, na.rm = T)/sqrt(n()),
             .groups = "drop")%>%
   mutate(trial = paste(location,year,sep = "\n"))%>%
   mutate(yield = ifelse(spray_NoSpray == "control", yield_c, yield_gain_m))%>%
   ggplot(aes(reorder(trial_ref, yield), yield, fill = (spray_NoSpray)))+
   geom_col()+
   # geom_errorbar(width = 0.3 ,aes(ymax = yield_gain_m + yield_gain_se, 
   #                   ymin = yield_gain_m - yield_gain_se))+
   theme(axis.text.x = element_text(angle = 90, hjust = 1))+
   scale_fill_usq() +
   scale_colour_usq()

>>>>

```{r ControlYield_AllTrials}
PM_MB_dat %>%
   filter(fungicide_ai == "control")%>%
   summarise(mean_yield = mean(grain_yield.t.ha. * 1000),
             minimum_yield = min(grain_yield.t.ha. * 1000),
             maximum_yield = max(grain_yield.t.ha. * 1000),
             yield_stdev = sd(grain_yield.t.ha. * 1000),
             yield_SE = sd(grain_yield.t.ha. * 1000)/
                              sqrt(n())) %>%
   kable(align = 'c',
   caption = "Average yield statistics for no spray contol plots"
)

@@

Trial mean yields in DMI fungicide treated plots
```{r Yield_DMITrials}
PM_MB_dat %>%
   group_by(trial_ref, location, year)%>%
   summarise(mean_yield = mean(grain_yield.t.ha.*1000),
             minimum_yield = min(grain_yield.t.ha.*1000),
             maximum_yield = max(grain_yield.t.ha.*1000),
             yield_sterr = sd(grain_yield.t.ha.*1000)/(sqrt(length(grain_yield.t.ha.))))%>%
   arrange(yield_sterr) %>%
   kable(align = 'c',
   caption = "Average yield statistics for DMI fungicide treated plots")

@@

```{r Yield_plot}

bw_labels <- 
   PM_MB_dat %>%
   filter(trial_ref %in% DMITrials)%>% 
   group_by(trial_ref, location, year)%>%
   summarise(m_gy = mean(grain_yield.t.ha.)) %>%
   mutate(trial = paste(location,year,sep = "\n")) %>%
   arrange(m_gy) %>%
   pull(trial)

bw_labels[1] <- paste0(bw_labels[1],"(b)")
bw_labels[3] <- paste0(bw_labels[3],"(a)")

fungicide_spray_plot <- 
   PM_MB_dat %>%
   filter(trial_ref %in% DMITrials)%>%  
   mutate(spray_treat = ifelse(fungicide_ai == "control","control", "DMI spray"))%>%
   group_by(trial_ref, location, year)%>%
   ggplot(aes(reorder(trial_ref, grain_yield.t.ha.), grain_yield.t.ha., colour = spray_treat))+
   geom_boxplot()+
   theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3))+
   xlab("Trial location and year")+
   ylab(bquote('Mungbean yeild  '*t~ha^-1*''))+
   scale_x_discrete(labels = bw_labels)+
   ylim(0,2.5)+
   scale_colour_usq()+
   labs(colour = "Fungicide treatment")
